---
title: "uscovid : COVID-19 in United States"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{uscovid}
  %\VignetteEngine{rmarkdown::render}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
library(uscovid)
```

The uscovid package is an R package which encloses a [shiny web application](https://aarathybabu.shinyapps.io/covid/). The web application showcases an overview of the data on COVID-19 on a global scale and also explores the test results as well as different dimensions of the effect of the pandemic in the United States of America. The package makes it possible for a user to launch the app locally which would aid the user in reproducing the web application. 

# Installation

You can install the development version from Github using:

```{r, eval = FALSE}
devtools::install_github("etc5523-2020/r-package-assessment-aarathybabu97")
```

# Usage 

The primary purpose of the **uscovid** package is to launch the enclosed web application locally. 

## Launching the App

The web application can be launched in the following way,

```{r app-launch,eval=FALSE}
#load the package

library(uscovid)

#use function launch_app()
launch_app() 

``` 

The function,**launch_app()** from the package, launches the web application *COVID-19 in United States*. The app aims to display the figures on confirmed cases, deaths and recoveries around the World with a focus on United States, which is one of the worst affected countries in the world. It also showcases the testing rate over the months in each state of US as well as the demographic trends of COVID-19 positive cases in US. 




