---
title: "uscovid : COVID-19 in United States"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{uscovid : COVID-19 in United States}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
library(uscovid)
```

The uscovid package is an R package which encloses a [shiny web application](https://aarathybabu.shinyapps.io/covid/). The web application showcases an overview of the data on COVID-19 on a global scale and also explores the test results as well as different dimensions of the effect of the pandemic in the United States of America. The package makes it possible for a user to launch the app locally which would aid the user in reproducing the web application. 

# Installation

You can install the development version from Github using:

```{r, eval = FALSE}
devtools::install_github("etc5523-2020/r-package-assessment-aarathybabu97")
```

# Usage 

The primary purpose of the **uscovid** package is to launch the enclosed web application locally.

## Functions and Datasets in package

- **launch_app()**  : Launches the shiny web application enclosed with the package.
- **selectin()**  : Displays the COVID-19 cases around the world and the testing rates in US states depending on the parameter selected.
- **sinput()**    : Calls selectInput() function from shiny r package where necessary which in turn creates a drop down menu from which values can be selected. 
- **printext()**  : Prints strings as texts.
- **choosevar()** : Selects a particular variable in a data frame after filtering observations to match a particular value.

The datasets include,

- **positive_cases**   : The dataset contains data on the cumulative COVID-19 positive cases for the US on individual state level .
- **codes**            : Data on the names of countries and its two digit state code.
- **months_tests**     : The dataset contains monthly test data on the COVID-19 pandemic for the US on individual state level

### Launching the App

The web application can be launched in the following way,

```{r app-launch,eval=FALSE}
#load the package

library(uscovid)

#use function launch_app()
launch_app() 

``` 

The function,**launch_app()** from the package, launches the web application *COVID-19 in United States*. The app aims to display the figures on confirmed cases, deaths and recoveries around the World with a focus on United States, which is one of the worst affected countries in the world. It also showcases the testing rate over the months in each state of US as well as the demographic trends of COVID-19 positive cases in US. 

### Usage of Other functions 

```{r selectin,eval=FALSE}

selectin("world",monthlist)
selectin("usa",statelist)


``` 


The function deploys a shiny app which the user can interact with. The parameters required for the function to display the global COVID-19 cases for each month is "world" along with monthlist where as parameters "usa" along with statelist displays the testing rates over the months in each state of US.

```{r sinput,eval=FALSE}

sinput("monthname","select a month",monthlist)
printext("text to be printed")
choosevar(codes,Afghanistan,Code)

``` 

The function sinput() returns a drop down menu with values in "monthlist" as options and "select a month" as its label compatible with shiny r package where as printext() prints "text to be printed".
In the above example, choosevar() returns the code of Afghanistan. 

# About the App

There are three main topic the web application aims to showcase,The confirmed cases, deaths and recoveries because of COVID-19 on a global scale,the testing streak as well as its results in the states of United States over the months. It always shows how different groups of population in the US are affected by the pandemic. 

## COVID-19 Worldwide

An interactive table is employed to showcase the repercussions of COVID-19. The table represents the worldwide COVID-19 cases,deaths and recoveries each month and allows the user to search for the country and month of their choice as well as arrange them in the order using the parameters of their choice. For example, Confirmed Cases. User can also view some information like life expectancy, population density etc on the countries by selecting them.

## COVID-19 Testing

COVID-19 cases in the US is explored by an interactive map showcases the total number of positive cases in each state of United States by hovering over each state where as the point graph depicts the COVID-19 tests conducted in each state during a month.The user can see testing streak of each state and the percentage of positive cases in that state and during a particular month by clicking on its corresponding point in a scatterplot figure. 

## Demographic Trends

A chart representing the gender,racial identity as well as the age group under which the COVID-19 positive patients fall is employed to highlight the trends in COVID positive cases. The user is allowed to explore the demographic trends in the COVID-19 positive cases by choosing a parameter. 


